From physical principles to ???

### 2016-04-29 2015CompleteDerivation/completeDerivation.tex
Comment on conservative forces and detrev
First stab at the measure justification

As we combine parts, the total amount of material will be the sum of the material of the parts. As we increase or decrease by a constant factor the total amount of material in a state, we will find the total amount of material of that state increased or decreased by that factor. That is: $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$. For a proper state, one that is not the difference of two states, we will expect a positive amount of material. So, if a density $\rho_\mathcal{c}$ is positive everywhere, then the total amount is also positive. This makes $\Lambda_U$ a positive linear functional. As the amount of material we will measure is always finite, the functional applied to any composite state $\mathcal{c}$ over any set $U$ will be finite.

@@

\begin{justification}
	TODO
\end{justification}

@@

We recognize the familiar set of Hamilton's equations. They are the set of equation to describe the deterministic and reversible motion of the infinitesimal parts of an infinitesimally reducible homogeneous material. The challenge in their derivation mainly lies in the necessary use of different branches of mathematics (e.g. topology, measure theory, differential geometry, symplectic geometry). The conceptual meaning, on the other hand, is hopefully straight forward.

>>>>

As we combine parts, or increase the amount of material in each part, the total amount of material found will have to be consistent with those operations. That is: $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$. For a proper state, one that is not the difference of two states, we will expect a positive amount of material. So, if a density $\rho_\mathcal{c}$ is positive everywhere, then the total amount is also positive. This makes $\Lambda_U$ a positive linear functional. As the amount of material we will measure is always finite, the functional applied to any composite state $\mathcal{c}$ over any set $U$ will be finite.

@@

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each open set $U \subseteq \mathcal{S}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. Let $U_1, U_2$ two disjoint sets, then $\Lambda_U = \Lambda_{U_1} + \Lambda_{U_2}$ as the material found in $U$ must be either in $U_1$ or $U_2$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of distribution at each particle state is positive then the total amount of material is positive.

	We claim that $\mathcal{S}$ is endowed with a Borel measure $\mu$. $\mathcal{S}$ is locally compact as it is a manifold. At each point there exists an compact open a neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff space on which is defined a positive linear function $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous compactly supported real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. $\Lambda_U$ is the sum for disjoint subsets, therefore $\Lambda_V (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$ for any open set $V \supseteq U$. The measure is unique in the family of all functionals $\Lambda_U$. $\Lambda_U(\mathcal{c})$ is finite for any open, therefore $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.
\end{justification}

@@

We recognize the familiar set of Hamilton's equations. They are the set of equation to describe the deterministic and reversible motion of the infinitesimal parts of an infinitesimally reducible homogeneous material. In other words: \textbf{the forces that conserve energy (i.e. the value of a sutiable Hamiltonian) are exactly the ones that provide deterministic and reversible motion}. The challenge in their derivation mainly lies in the necessary use of different branches of mathematics (e.g. topology, measure theory, differential geometry, symplectic geometry). The conceptual meaning, on the other hand, is hopefully straight forward.
